---
title: "Journals publishing software papers in ecology, evolution & environment"
output: 
  html_document: 
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<br>

A crowd-sourced directory of journals publishing **software papers** related to ecology, evolution & environment: 

Check out the [Software Sustainability Institute](https://www.software.ac.uk/which-journals-should-i-publish-my-software) for a more comprehensive list (all disciplines). 

For Data Papers, check out GBIF directory of journals publishing biodiversity-related [Data Papers](https://www.gbif.org/data-papers).

## Journals

```{r message=FALSE, echo=FALSE, warning=FALSE, out.width="100%"}
library(dplyr)
library(DT)

df <- readr::read_csv("journals_software_ecology.csv") %>% 
  mutate(journal = paste("<a href='", Website, "'", ' target="_blank">', 
                            Journal, "</a>", sep = "")) %>% 
  select(-Website) %>% 
  mutate(Issn = stringr::str_remove(ISSN, "-"))

sjr <- readr::read_csv2("scimagojr2020.csv") %>% 
  select(Issn, SJR, `SJR Best Quartile`) %>% 
  tidyr::separate(Issn, into = c("Issn1", "Issn2"), sep = ", ") %>% 
  mutate(issn1 = Issn1 %in% df$Issn,
         issn2 = Issn2 %in% df$Issn) %>% 
  filter(issn1 == TRUE | issn2 == TRUE) %>% 
  mutate(Issn = ifelse(issn1 == TRUE, Issn1, Issn2)) %>% 
  select(Issn, SJR, `SJR Best Quartile`)
  

journals <- left_join(df, sjr, by = "Issn") %>% 
  arrange(Journal) %>% 
  select(-Journal, -ISSN, -Issn) %>% 
  rename(Journal = journal,
         `Scimago\nJournal Rank` = SJR) %>% 
  relocate(Journal)


DT::datatable(journals, escape = FALSE, #filter = "top",
              options = list(pageLength = 20))
```

OA (Open Access):

  - Yes: All articles are published open access
  
  - Hybrid: Some articles are published open access, usually after paying an Article Processing Change (APC) fee. 
  
Article Processing Charges (APC) may not be up to date. Also, many journals offer fee waivers and discounts. Please check the journal website.

Journal Rank data from [Scimago](https://www.scimagojr.com/journalrank.php). Please visit [their website](https://www.scimagojr.com/journalrank.php) for more details.

### Contributing

If you find an error or want to add new journals, please open an issue or a pull request [on GitHub](https://github.com/Pakillo/journals-software-ecology).


Last update: `r Sys.Date()`
